---
title: "Vignette 1"
author: "Abhinav Piplani"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Vignette Info

This vignette provides a meaningful description of the package Assignment 1 and how it should be used. The usage of all the functions a re decsribed one by one



```{r,   message=F, warning=F}
 library(readr)
 library(dplyr)
 library(tidyr)
 library(maps)
library(knitr)
library(tidytext)

library(Assignment1)

# opts_knit$set(root.dir=normalizePath('../'))

```

Read Data for accidents occuring in 2013



```{r, message=F, warning=F}
# attach(accidents.2013)
# mydata <- accidents.2013

#mydata <-read.csv(system.file(file.path("exdata","accident_2013.csv.bz2"), package="Assignment1"))
  #read.csv("accident_2013.csv.bz2")

mydata <- fars_read("accident_2013.csv.bz2")
#mydata <- fars_read(system.file(file.path("exdata","accident_2013.csv.bz2"), package="Assignment1"))
str(mydata)
#mydata <- fars_read_years(2014)
```


Generates a filename (character) in the format similar to other files given as a part of the 1st
assignment of the course 'Building R Packages" on Coursera.



```{r, message=F, warning=F}
myfilename <- make_filename(2020)

```

Subsetting Year & Month variables from the data for 2014


```{r, fig.show='hold'}
  mydata <- fars_read_years(2014)
  #mydata <- fars_summarize_years(2013)
  str(mydata)
```


Summarizes Year & Month variables from the data for year 2014 

```{r, fig.show='hold'}
 mydata <- fars_summarize_years(2014)
 str(mydata)
```


Plots accidents on a state map for state number 55, year 2013

```{r, fig.show='hold'}
 mydata <- fars_map_state(55, 2013)
  str(mydata)
```


